---
title: "Machine Learning: Linear Regression"
author: "Ph.D. Pablo Eduardo Caicedo R."
date: Octubre, 2022
logo: ./Logos/logo-small-small-black.png
output:
    beamer_presentation:
        keep_tex: true
        theme: metropolis
        fonttheme: structuresmallcapsserif
        latex_engine: xelatex
        incremental: no

header-includes:
    \hypersetup{colorlinks,citecolor=orange,filecolor=red,linkcolor=brown,urlcolor=blue}
    \usepackage{booktabs}
    \usepackage{longtable}
    \usepackage{array}
    \usepackage{multirow}
    \usepackage{wrapfig}
    \usepackage{float}
    \usepackage{colortbl}
    \usepackage{pdflscape}
    \usepackage{tabu}
    \usepackage{threeparttable}
    \usepackage{threeparttablex}
    \usepackage[normalem]{ulem}
    \usepackage{makecell}
    \usepackage{xcolor}
---

```{r setup, include=FALSE}
library("reticulate")
use_condaenv("dsenvpy310")
knitr::opts_chunk$set(echo = FALSE)

def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})

```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Slide with python
\tiny
```{python, echo=TRUE}
import sys
import pandas as pd
data = pd.read_csv("/Users/pacaicedo/DatasetsVault/Income/income2.csv",delimiter=",", decimal=".")
data.Income.hist()
```
\normalsize